### 2021-05-10 yfcc100m/paper/vldb2021/submission/review_response/reviews_response.tex

%===========================================================
\section{General Description of Changes}
%===========================================================

The authors would like to thank the program committee and the reviewers
for the comments and suggestions,
instrumental to increase the quality of our work and its presentation.

We have addressed comments from every reviewer separately, but the following
list summarize the main updates:

\begin{itemize}
  \item We have added and run a new experiment that compares VDMS and baseline
        for queries that do not run a pre-processing operations, following
        reviewer's suggestions.
        We expand the analysis of the results including these findings.
  \item We have expanded on the type of supported pre-processing
        operations, and more details on VDMS API design in general.
  \item We have expanded on the description of the ACID properties offered
        by VDMS and how that mechanism work.
  \item We have expanded on the type of queries supported by VDMS,
        including similarity-search based on feature vectors,
        which is a feature currently supported by the system.
  \item We have added a "Future Work" sections where we describe some
        of the limitations found during these experiments, as well as the
        near and long term line of work after this paper.
\end{itemize}

@@

%===========================================================
\section{Reviewer \#1}
%===========================================================

\noindent %
\textbf{
D1 (W1): Although VDMS mentions that it supports Visual Feature Vectors as
first class citizens in Section 3.3, the queries used in evaluation
do not include an example.
}\bigskip

Thanks for your comment.
Following feedback and suggestions from last year's submission at this same venue,
we decided to skip the feature vector functionality evaluation and
focus on image search based on metadata to compare
against well-known baselines better.
We should note that similarity search based on feature vectors
is fully implemented, and you can find the more details on the project's wiki
\footnote{https://github.com/IntelLabs/vdms/wiki/Descriptors-Tutorial}
\footnote{https://github.com/IntelLabs/vdms/wiki/FindDescriptor}.

Including an analysis of similarity search in this same work would also
complicate the implementation of the baselines, making it harder to understand
and isolate the main sources of performance gains.
We have a preliminary implementation of baselines for our internal use cases,
and it meant combining more than 4 systems (SQL database, web server, client side
pre-processing with OpenCV, some quick-and-dirty implementation
to provide client-server architecture to Faiss/Annoy, given that these
are just C++ libraries).
This increases the complexity of the baseline systems, adding
more parameters to tune, and complicating the understanding of the results.
We have decided to focus this work on image search based on metadata tags
and the addition of needed pre-processing operations, and
work on a similarity-search specific evaluation as a next step.
If reviewers are interested in learning more about our similarity search functionality,
we have attached, as an appendix, part of the evaluation we submitted last year.
It also includes initial evaluation on the Video API, which works in a very
similar way as it does for images.
We will continue to improve this evaluation, and submit to arxiv directly
as an extension of this work.

@@

\bigskip
\noindent %
\textbf{
D2 (W1): All queries involve “resize” operation, which is expensive for the
baselines since it is happening on the client side.
A simplistic query without resizing can show how the graph model performs
against traditional RDS DBs (i.e., will show that VDMS has comparable
performance even for such use-case without "visual manipulation").
}\bigskip

This is a great point, we very much appreciate the suggestion.
We have run a new experiment and added a new figure to the paper (Figure 9),
where we compare 3 of the queries with and without the resize operation
to understand the difference in performance better.
We have also added an explanation on these differences in performance
in the final version, and made these results publicly available
\footnote{https://github.com/luisremis/visual\_storm/tree/master/yfcc100m/python/eval/results/resize\_comparison}
(as the rest of the evaluation in this work).
Note that, even if the resize happens on the client side in the case of both
baselines we have built, the computing capabilities of the server and the
client are identical.
This is on purpose, to avoid the difference in computing power for the
resize operation to affect the understanding of the results.

\bigskip
\noindent %
\textbf{
D3 (W2): It is not clear which queries are supported or not.
The queries used for evaluation are based on tags and geo search.
What about visual-based queries? For example, is image similarity search based
on Visual Feature Vectors within a geographical region supported?
}\bigskip

VDMS does support the suggested query, i.e., perform a similarity search based
on feature vectors and also filter by geographical location.
This can be achieved using very similar queries as the one used in
the present evaluation, plus the use of the feature vector queries,
that are natively supported using the same set of APIs (as we mention in D1).
Because of space constraints, we were not able to accommodate initial evaluation
we have been working on for Feature Vector-based search specifically,
and we plan to perform a more comprehensive evaluation on this functionality
of this feature because of its relevance when processing visual data, as well
as our own needs in our use cases.

@@

\noindent %
\textbf{
D1. The proposed solution seems to use the functionalities of the existing systems
as it is. Authors should provide more original ideas or more innovative designs.
For example, providing optimizations that specifically target visual data or query
patterns associated could have been more meaningful to the research communities and
convince users to replace their customized solution to VDMS.
}\bigskip

Thanks for your comment, these are important clarifications to add.
We have expanded on additional details on which operations we support and our
decision for choosing the operations in Section 3, and how supporting
these operations natively opens optimization possibilities that we exploit.
We also elaborated more on the benefits of
using VDMS over ad-hoc solutions in Section 3.1.
We avoided expanding on supported operations for images due to space constraints,
and because these are fully documented on the project's wiki
\footnote{https://github.com/IntelLabs/vdms/wiki}.
The wiki also contains the full documentation on APIs for video and similarity
search, among other things, which work together with the API we used for
image search for this work, providing a unified API for all the data applications need.

\bigskip
\noindent %
\textbf{
D2. Both baselines are similar in architecture, and the evaluation has not effectively
highlighted the performance gain of other design choices authors made in VDMS,
except that the VDMS server process both metadata operation and image operation
within only one round of communication with clients.
For example, benchmarking systems can be built to test in isolation the
improvement on metadata handling.
}\bigskip

Thank you for the input.
To demonstrate the benefits of VDMS more clearly, we have added Figure 9,
which compares queries with and without the resize operation.
Without the resize operation, the evaluation shows the
improvement on metadata handling better, plus the effect of a single round
of communication between client and the server (as it is the case with VDMS).
Because we design VDMS for visual data as the first class elements,
we focused our evaluation on the retrieval of visual objects rather
than metadata only.
When it comes to building solutions that primarily depend on metadata,
rather than actual visual objects, the authors believe that VDMS is not
the right solution, given that there are many other commercially available
solutions (relational databases, graph databases, document-oriented databases, etc.)
that have been optimized over many decades and provide a level of
functionality and maturity that is sufficient for the majority of the use cases.

### 2021-05-10 yfcc100m/paper/vldb2021/intro.tex
Minor changes to intro

Despite the increasing use of visual data processing,
there has been very little research on the \textit{management} of visual data.
Most of the current storage solutions for visual data are an ad-hoc collection
of tools and systems, that are re-purposed and adapted to work with visual data.
The approach of re-purposing and integrating solutions not designed for a task
results in resource utilization inefficiencies\cite{rasdaman}.
The combination of systems is required to manage both \textit{metadata} and
\textit{visual data}.
We use \textit{visual data} to refer to any pixel-data (images, videos,
frames in a video, etc), and feature vectors (a.k.a. descriptors, or embeddings),
which are representations of the pixel data.
We use \textit{metadata} to refer to any data that is important within
the context of specific applications.
Information about a patient (name, last name, unique identifiers), or
about a clinic (name, location, etc) are examples of what we refer to
as \textit{metadata} in the context of a health-care IT system.
One can think of \textit{metadata} as the data an application would store
in rows and tables following the relational model.

To illustrate the point on the need for multiple systems to build the data
infrastructure for applications,
consider a ML developer constructing a pipeline for extracting
brain tumor information from existing brain images in a classic medical
imaging use case.
This requires assigning consistent identifiers for the scans and adding their
\textit{metadata} in a relational or key-value database\cite{kumar2017data}.
If the queries require a search over patient information,
then patients are associated with their brain scans.
Finally, if the ML pipeline needs images with a different resolution
than the original, there is additional compute
diverted towards pre-processing the original images.
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with many scripts for this specific use case.
Moreover, if the pipeline identifies new metadata to be added for
the tumor images, most databases make it hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch, qin2020similarity}
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a
subset of the data before running any processing, and a large effort
is devoted to filtering, curating, and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc), and
building the necessary pipelines for querying and retrieving the right data.

>>>>

Despite the increasing use of visual data processing,
there has been very little research on the \textit{management} of visual data.
Most of the current storage solutions for visual data are an ad-hoc collection
of tools and systems, that are re-purposed and adapted to work with visual data.
The approach of re-purposing and integrating solutions not designed for a task
results in resource utilization inefficiencies\cite{rasdaman}.
The combination of systems is required to manage both \textit{metadata} and
\textit{visual data}.
We use \textit{visual data} to refer to any pixel-data (images, videos,
frames in a video, etc.), and feature vectors (a.k.a. descriptors, or embeddings),
which are representations of the pixel data.
We use \textit{metadata} to refer to any data that is important within
the context of specific applications.
Information about a patient (name, last name, unique identifiers), or
about a clinic (name, location, etc.) are examples of what we refer to
as \textit{metadata} in the context of a health-care IT system.
One can think of \textit{metadata} as the data an application would store
in rows and tables following the relational model.

To illustrate the point on the need for multiple systems to build the data
infrastructure for applications,
consider a ML developer constructing a pipeline for extracting
brain tumor information from existing brain images in a classic medical
imaging use case.
This requires assigning consistent identifiers for the scans and adding their
\textit{metadata} in a relational or key-value database\cite{kumar2017data}.
If the queries require a search over patient information,
then patients are associated with their brain scans.
Finally, if the ML pipeline needs images with a different resolution
than the original, there is additional compute
diverted towards pre-processing the original images.
All these steps require understanding different software
solutions that provide various functionalities that can then be stitched
together with many scripts for this specific use case.
Moreover, if the pipeline identifies new metadata to be added for
the tumor images, most databases make it hard to change the schema on the fly.
As another example, many applications can be studied through the use of large
and publicly available datasets.
Applications include basic image search functionality (through the use
of human-generated tags), advanced image search through the use of
machine-generated tags and feature vectors\cite{imagesearch, qin2020similarity}
for each image, and video summarization.
For these use-cases, the usual first step consists on selecting a
subset of the data before running any processing, and a large effort
is devoted to filtering, curating, and pre-processing the data.
Selecting subsets of data is by itself a time consuming task,
as it involves loading all metadata into a solution that enables searching
based on tags (relational database, graph database, csv files, etc.), and
building the necessary pipelines for querying and retrieving the right data.
